\dirtree{%
.1 bachelor\_scripts/.
.2 pattern\_mining/.
.3 first\_versions/ \DTcomment{First-iteration boundary mining and motif scoring}.
.4 motif\_score.py.
.4 subroutine\_boundaries\_csv.py.
.3 v2/ \DTcomment{Second-iteration prologue/epilogue miner with JSON/text reports}.
.4 prologue\_epilogue\_miner\_v2.py.
.4 patterns\_v2.json.
.4 pattern\_report\_v2.txt.
.4 region\_details\_v2.txt.
.3 v3/ \DTcomment{Third-iteration miner with grouped and combined reports}.
.4 prologue\_epilogue\_miner\_v3.py.
.4 patterns\_v3.json.
.4 pattern\_report\_v3\_combined.txt.
.4 pattern\_report\_v3\_groupA.txt.
.4 pattern\_report\_v3\_groupB.txt.
.4 region\_details\_v3.txt.
.2 analysis\_out/ \DTcomment{Aggregated JSON and CSV outputs from the first-iteration miner}.
.3 boundary\_patterns.json.
.3 candidate\_scores.csv.
.3 candidate\_scores.json.
.2 code\_analysis/.
.3 file\_similarity/ \DTcomment{Byte-frequency histograms and similarity matrices}.
.4 bytefreq\_per\_device.py.
.4 out\_freq/.
.5 bytefreq\_by\_device.csv.
.5 similarity\_chi2.csv.
.5 similarity\_jsd.csv.
.5 similarity\_sorted\_cosine.csv.
.3 code\_similarity/ \DTcomment{Thumb code-region filter and code-only similarity outputs}.
.4 thumb\_code\_only\_histograms.py.
.4 out\_code/.
.5 code\_only\_bytefreq\_by\_device.csv.
.5 code\_only\_similarity\_chi2.csv.
.5 code\_only\_similarity\_cosine.csv.
.5 code\_only\_similarity\_jsd.csv.
.5 code\_only\_summary.json.
.3 candidates\_inside\_code\_regions/ \DTcomment{Candidate-vs-code-region overlap check}.
.4 check\_candidates\_in\_code\_regions.py.
.4 thumb\_return\_signatures.py.
.4 out\_candidates/.
.5 candidate\_code\_region\_hits.csv.
.5 candidate\_code\_region\_summary.csv.
.4 out\_code/.
.5 thumb\_return\_signatures\_offset6001.csv.
.3 codeonly\_bins/ \DTcomment{Code-only binary extraction and generated blobs}.
.4 make\_codeonly\_blobs.py.
.4 out\_codeonly/ \DTcomment{Generated code-only .bin and mapping .csv files}.
.3 periodicity\_autocorr/ \DTcomment{Autocorrelation-based periodicity analysis}.
.4 periodicity\_autocorr\_v3.py.
.2 entropy\_plot/ \DTcomment{Entropy visualisation script}.
.3 entropy\_plot.py.
.2 changelog\_crawl\_script/ \DTcomment{Web scraper and scraped Shimano firmware changelogs}.
.3 shimano\_crawl.py.
.3 shimano\_firmware\_changelogs/.
.4 DU-E5000.txt.
.4 DU-E6001.txt.
.4 DU-E6002.txt.
.4 DU-E6100.txt.
.4 DU-E8000.txt.
.4 SC-E6010.txt.
.2 disasm/ \DTcomment{Disassembly of 3 firmware files}.
.3 due5000.4.1.0.dissasm.txt.
.3 due6100.4.1.1.dissasm.txt.
.3 due8000.4.0.1.dissasm.txt.
.2 diff.csv \DTcomment{Original dataset with 148 candidates}.
.2 filtered.csv \DTcomment{Refined dataset with 103 candidates}.
}
